Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
section relevant approaches WIP

@@

\begin{abstract}
    \begin{center}
        (Some distant lyrics as the placeholder of the actual abstract)

@@

\begin{quotation}
The function of money is to facilitate the business of the market by acting as a common medium of
exchange. \footfullcite[][Chapter One, Chapter I, § 1, p1]{von2013theory}
\end{quotation}

@@

This paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of how money
can perform its function of medium of exchange using computer science.

@@

We call these money mediums. And we further separate them into two big groups:

\begin{itemize}
\item \textit{Token and Its Accounts} - E.g. bank currency accounts. Each token is its own centralized execution
    environment, bearers access their monetary value through their accounts, and execute financial contracts through the
    token.
\item \textit{Note} - E.g. federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
    independent of the notes, but it needs notes to complete the execution of financial contracts.
\end{itemize}

@@

\subsection{Constraint Programming}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

>>>>

%% Formattings

\renewcommand{\mkbegdispquote}[2]{\itshape}

@@

\begin{abstract}
    \begin{center}
        (Some distant lyrics as the placeholder for the actual abstract)

@@

\begin{displayquote}
The function of money is to facilitate the business of the market by acting as a common medium of
exchange. \footfullcite[][Chapter One, Chapter I, § 1, p1]{von2013theory}
\end{displayquote}

@@

This paper adds a new controversy to money, that is to present a survey challenging the preconceived notion of how money
can perform its function of medium of exchange.

@@

We call them money mediums, and we further separate them into two big groups:

\begin{itemize}
\item \textit{Token and its Accounts} - E.g. bank currency accounts. Each token is its own centralized execution
    environment, bearers access their monetary value through their accounts, and execute financial contracts through the
    token.
\item \textit{Note} - E.g. federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
    independent of the notes, but it needs notes to complete the execution of financial contracts.
\end{itemize}

@@

The focus of this paper is to formally define a set of payment primitives that modernize our payment systems. To prevent
reinventing wheels, it is relevant to discuss first some approaches in computer science that are believed to help
solving this challenge.

@@

Recall that we want our modernized payment system to handle money distribution continuously over time, and its financial
contracts compositional. A very closely related software design paradigm best known to address those needs is
\textit{functional reactive programming (FRP)}. It was first introduced by Conal Elliott \& Paul Hudak in solving multimedia
animations \cite{elliott1997functional}. Later on, Hudak also worked on \cite{hudak2002arrows} and
\cite{wan2000functional} making FRP a more general framework for programming hybrid system with continuous behaviors in
a high-level, declarative manner.

After FRP got more adoption, it evolved to some variations that support discrete semantics, and some variations better
suited more for interactive systems. In this paper we will stick to and revisit the original formulation use in
\cite{elliott1997functional} where we will draw inspirations from.

... TODO

@@

We also want a formal and precise specification of payment primitives. The title of the paper mentions denotational
semantics, it is a \textit{compositional} style for precisely specifying the meanings of languages, invented by
Christopher Strachey and Dana Scott in the 1960s (\cite{scott1971toward}). Conal Elliott proposed that denotational
semantics can also be applied to \textit{data types} in programming \footfullcite[][section 2, denotational semantics
    and data types]{Elliott2009-type-class-morphisms-TR}. We will revisit this formulation too.

... TODO
